---
title: "20180119 GrNH2 mass production"
---

```{r, child="_setup.Rmd"}
```

As more graphene is needed, the production procedure from [20180110](20180110_GrNH2_production.html) will be repeated.

# Journal
1500 mL 0.1 M H~2~SO~4~ was made by diluting 150 mL 1.0 M H~2~SO~4~ to 1500 mL and then dissolving 2420 mg 4-(2-ammonioethyl)benzenediazonium salt first in 100 mL solution and then adding it to the rest. This was added to the electrochemical cell and cooling starting by flowing cold ethanol through a stainless steel pipe in the solution. 

A stock solution of 2-Naphthol was made by dissolving 12.0 mg in 10 mL 10 % NaOH and 40 mL H2O. An Ar ballon was attached to this to keep oxygen out. 1 mL samples from the exfoliation solution were extracted at regular intervals and mixed with 9 mL 2-naphthol solution. A syring filter was used to remove graphene. 

A graphene foil (Alfa Aesar, 0.5 mm x 8 cm x 15 cm) was attached to the power supply and mounted in the solution between two stainless steel electrodes.

Several batches were made:

```{r}
library(tidyverse)

experiments <- tribble(
  ~name, ~m_graphite, ~diazo_inital, ~diazo_final, ~m_wet,
  "20180119_1_A", 6.9565, 5, NA, 350.79 - 243.68,
  "20180119_1_B", 6.9747, NA, NA, 381.17 - 242.83,
  "20180119_2_A", 6.9486, 5, NA, 365.53 - 243.28,
  "20180119_2_B", 6.9869, NA, NA, 372.91 - 243.54
)

knitr::kable(experiments, format = "html", col.names = c("Sample name", "Graphite mass (g)", "Initial diazo (mM)", "Final diazo (mM)", "Wet mass of exfoliate (g)"), caption = "In reality concentrations needs to be calibrated with later UV-Vis measurements") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```


*20180119_1_A* graphite was lowered into solution at ca. 40 minutes to utilise a larger amount of the graphite. 
*20180119_1_B* is made by reusing the solution from the previous exfoliation but with new graphite. The solution was filtered to remove graphite and a new exfoliation started as soon as possible. Approx. 150 mL 0.1 M H~2~SO~4~ was added to make up for lost solvent. 
*20180119_2_A* I ran out of diazonium salt so only 2.0958 g was added, making the concentration approx 4.33 mM. 
*20180119_2_B* was made in in the same way as *1B*.

### Washing procedure
All collected graphite was washed with 2 x 500 mL H2O, 1 x 500 mL acetonitrile and 1 x 500 mL H2O. In all cases the graphite was stirred with the solvent and filtered again to ensure proper washing. 

# Results and discussion

# Conclusion and outlook
