# 20171020 Gr-NH2 production repeated {#j20171020}

This experiment is a repetition of [20170929](#j20170929), as several aspects of the experiment failed to work as expected. By a few simple modifications, it will hopefully be possible to 1) monitor diazonium concentration, and 2) obtain a proper freeze-dried product. 

## Protocol
```{r stochiometry171020}
library(units)
V = set_units(1500, mL) # Volume of 0.1 M H2SO4 to be used
C_diazo = set_units(2, mmol/L)
C_naphtol = set_units(3, mmol/L)
V_naphtol = set_units(30, mL)

M_nitro = set_units(202.64, mg/mmol) # 4-Nitrophenethylamine hydrochloride
M_nitrite = set_units(69.00, mg/mmol) # NaNO2
M_naphtol = set_units(144.17, mg/mmol) # 2-Naphtol

n_nitro = V * C_diazo
n_nitrite = n_nitro * 2
n_naphtol = V_naphtol * C_naphtol # enough to make 15 samples of 2 mL

m_nitro = n_nitro * M_nitro
m_nitrite = n_nitrite * M_nitrite
m_naphtol = n_naphtol * M_naphtol

C_dye = set_units(C_diazo * set_units(2, mL) / set_units(4, mL), mmol/L)
```

### Preparing solutions
`r format(V*0.1 / 1.0)` 1.0 M H~2~SO~4~ is diluted to `r format(V)` to produce 0.1 M H~2~SO~4~. 

The `r format(C_diazo)` 4-(2-aminoethyl)benzenediazonium solution is generated *in-situ* by mixing `r format(V)` 0.1 M H~2~SO~4~ with `r format(m_nitro)` 4-Nitrophenethylamine hydrochloride (`r format(n_nitro)`) and `r format(m_nitrite)` NaNO~2~ (`r format(n_nitrite)`). This is stirred for 15 min.

A `r format(C_naphtol)` solution of 2-Naphtol is made by dissolving `r format(m_naphtol)` mg 2-Naphtol in `r format((1/5)*V_naphtol)` 10 % NaOH and `r format((4/5)*V_naphtol)` H~2~O.

Samples for UV-Vis can then be made easily by mixing 2 mL `r format(C_naphtol)` 2-Naphtol solution with 2 mL `r format(C_diazo)` diazonium-solution to obtain a solution of the azo-dye (max conc. obtained is 1 mmol/L).

### Gr-NH~2~ exfoliation
The electrochemical exfoliation of functionalised graphene will be done by positioning and 8x15 cm^2^ graphite foil between two large stainless steel electrodes and applying 10 V for 1 hour or more. Weigh the foil before electrolysis.

2 mL samples will be extracted with a syringe and put into the 2-Naphtol solution through a filter (to remove any graphite) every 20 minutes. At these points the temperature should also be noted. The samples are put in a 50 °C water bath for 2 minutes to facilitate reaction, before measuring the UV-Vis absorption.

The exfoliated graphene and remaining graphite foil is collected and washed several times with water  (mix thoroughly with water, measure pH of the filtrate). Keep most of the graphene at this point and work from here only in smaller batches to test the freeze-drying procedure.

The graphene is ultrasonicated in DMF (perhaps ca. 1 g / 100 mL) and left overnight for graphite to sediment. 

The upper 95 % of the solution is collected and centrifuged to collect most of the graphene. It is then ultrasonicated in water and freeze-dried.

## Journal
The graphene was exfoliated as described in the protocol. Before exfoliation, graphite was expanded by submersing in liquid nitrogen for 30 s, followed by immersion in ethanol. This makes the foil expand to ~4 times the thickness. It was noted, however, that the current recorded was not significantly higher than [previous experiments](#j20170929), meaning that the exfoliation might be diffusion-limited at this point. 

The graphite foil weighed 7.07 g prior to exfoliation. 

Samples for UV-Vis were extracted every 20 min. At 80 min a new solution of diazonium-salt was made (although not with super accurate amounts, and probably let to react for too short time) to test the whether the 2-Naphtol solution was still active. Similarly, at 100 min a fresh 2-Naphtol solution was made to test properly for the final diazonium concentration. 

The exfoliated graphite was repeatedly washed with water (500 mL, completely mixing graphite and water) and filtrated until the pH was ca. 6.

## Results and discussion
```{r}
data171020 <- read_csv('../data/raw_data/electrochemistry/20171020_Gr-NH2_exfoliation.csv')
knitr::kable(data171020, col.names = c("Time (min)", "Temp. ($^{\\circ}$C)", "Voltage (V)", "Current (A)"))
```

### UV-Vis

```{r uvvis171020}
path <- "../data/raw_data/uvvis/20171020_GrNH2_azodye/"
specs170929 <- tibble(files = list.files(path = path, pattern = "*.csv")) %>% 
  mutate(time = stringr::str_extract(files, "[:digit:]*(?=min)") %>% as.numeric()) %>% 
  separate(files, into = c("date", "t", "extra"), sep = "_", fill = "warn", remove = FALSE) %>% 
  mutate(data = map(paste0(path, files), read_delim, delim = ";", skip = 1)) %>% 
  left_join(data171020, by = "time") %>% 
  unnest() %>% 
  mutate(region = ifelse(nm > 400, "Vis", "UV")) 

refspec <- read_delim('../data/raw_data/uvvis/20170915 Azodye/Azo-dye 1-0.csv', delim = ";", skip = 1) %>% 
  mutate(region = ifelse(nm > 400, "Vis", "UV")) 

specs170929 %>% 
  mutate(time = as.factor(time)) %>% 
  filter(is.na(extra), region == "Vis") %>% 
  ggplot() + 
  geom_vline(xintercept = 499) +
  geom_line(data = refspec, aes(nm, A), size = 1.5, alpha = 0.66) +
  geom_line(aes(nm, A, color = time, group = files)) +
  #scale_color_brewer(palette = "Paired") +
  scale_x_continuous(limits = c(400,700)) +
  scale_y_continuous(limits = c(0,0.3)) +
  labs(x = "Wavelength (nm)", y = "Absorption (a.u.)", title = "Absorption spectra for azo-dyes obtained throughout the exfoliation", subtitle = "The shaded grey line is the spectrum obtained on 20170914 as reference")

ggsave("../figs/20171020_UV-Vis_1.png", width = 16, height = 6, dpi = 300, units = "cm")
```


```{r fig.height=4.5}
g1 <- specs170929 %>% 
  filter(nm == 499) %>% 
  ggplot(aes(time, A, color = extra)) +
  geom_point() + 
  geom_line() +
  theme(legend.position = "top", axis.text.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(y = "Absorbance (a.u.)") +
  scale_x_continuous(breaks = seq(0, 100, 20)) +
  labs(title = "Absorption at 499 nm")

g2 <- specs170929 %>% 
  ggplot(aes(time, temp)) +
  geom_point() +
  geom_line() +
  labs(x = "Time (min)", y = "Temp (°C)") +
  scale_x_continuous(breaks = seq(0, 100, 20)) +
  scale_y_continuous(breaks = c(30, 45, 60)) 

cowplot::plot_grid(g1, g2, align = "v", ncol = 1, rel_heights = c(2,1))
ggsave("../figs/20171020_UV-Vis_2.png", width = 16, height = 9, dpi = 300, units = "cm")
```

Spectra were obtained from the samples taken every 20 min, after reacting with 2-Naphtol solution for minutes at 40 $^{\circ}$C. In the figure above a previous spectrum of the same compound is included for reference. Indications of a peak at 499 nm is seen up until 40 min. At this point the temperature goes above 50 degrees, and the diazonium compound probably decomposes.  The increase in intensity (and thus concentration) at 20 min. could indicate that the diazonium-compound did not form completely before being heated a little bit. 

## Conclusion and outlook
