---
title: 'Biweekly report: Functionalised graphene for polymer composites'
author: "Emil Tveden Bjerglund"
date: "19 jan 2018"
output:
  pdf_document: default
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r child = 'biweekly_header.Rmd'}
```

# Planned experiments from last biweekly report

* Isolate the current batch of graphene and analyse it.
* Given that this production is succesful, I just need to run several more of the same as quickly as possible to deliver to Radisurf, SP Group and the Chemical Engineers.

# Large scale graphene production

* I now have a pretty solid procedure for large scale exfoliation of functionalised graphene. I can exfoliate approx. 5 g/hr, and then it takes another day to do ultrasonication, centrifugation and freeze-drying. 
* Current I am focusing on making amine-functionalised graphene for SP Group and Radisurf. 
* For all experiments I monitor the diazonium concentration by extracting samples and reacting with 2-Naphtol to form an azo-dye. This seems to work well, and allows us to know the exact concentration during exfoliation and how it develops during the experiment. 

I current have approx. 20 g that will be processed over the weekend to form the final graphene.

## Challenges
Currently the two main challenges in processing the graphene is ultrasonication and freeze-drying. 

Ultrasonication has been mostly solved by using a probe-type ultrasonicator at the inorganic department. It seems to work well, but I have not done extensive testing to optimise parameters (concentrations, time, volume).

Freeze-drying is still posing problems for me. Lately I have had succes with freeze-drying approx. 1 g of material in 100 mL water by spin-freezing in a 500 mL flask and wrapping the flask in paper an alu-foil to insulate it, before putting on the freeze-dryer. This seems to help with the samples drying, but I still sometimes have samples failing due to thawing, and that renders the produced graphene unusable, since it cannot easily be dispersed in solvents again. I still wish to scale this process up a couple of factors to make handling large samples easier. 

# Plan for the next two weeks
* Characterisation of the amine-functionalised graphene.
* Meetings with SP Group and Radisurf to discuss which experiments they will make with the graphene. 